Cross-validating mixed-effects models

### 2024-07-01 scratch/notes_georges/vignettes_drafts/cv-mixed_modified-edited.Rmd
Change temporary fix to GetResponse.glmmTMB to 2024-06-30 version

  # temporary fix

  GetResponse.glmmTMB <- function (model, ...)
  {
    y <- insight::get_response(model)
    if(is.matrix(y) && dim(y)[2] == 1) y <- as.vector(y)
    if (is.factor(y)) {
      levels <- levels(y)
      failure <- levels[1L]
      if (length(levels) > 2L) {
        message("Note: the response has more than 2 levels.\n",
                " The first level ('", failure, "') denotes failure (0),\n",
                " the others success (1)")
      }
      y <- as.numeric(y != failure)
    }
    if (!is.vector(y))
      stop("non-vector response")
    if (!is.numeric(y))
      stop("non-numeric response")
    y
  }
  assignInNamespace("GetResponse.glmmTMB", GetResponse.glmmTMB, ns = 'cv')

>>>>

  # temporary fix 
GetResponse.glmmTMB <- function (model, ...){
   y <- insight::get_response(model)
   if (length(dim(y)) == 2 && dim(y)[2] == 1) y <- y[, 1]
   if (!is.vector(y))
     stop("non-vector response")
   if (!is.numeric(y))
     stop("non-numeric response")
   y
}
assignInNamespace("GetResponse.glmmTMB", GetResponse.glmmTMB, ns = 'cv')
